%\cvsection{Life Philosophy}
%\begin{quote}
%``All we have to decide is what to do with the time that is given to us.'' - Tolkien
%\end{quote}

\cvsection{Education}

\cveventsidebar{B.S.\ in Actuarial Science}{Simon Fraser University}{Sep 2012 -- Apr 2017}{Burnaby, BC}

%\vspace{5mm}

\begin{itemize}
\item Actuarial science is a blend of mathematics, statistics, finance, economics and computer science.
\end{itemize}

%Core Material:
%\vspace{-3mm}
%\begin{multicols}{2}
%\begin{itemize}
%\item Mathematics
%\item Statistics
%\item Finance
%\item Economics
%\item Computer Science
%\end{itemize}
%\end{multico

%\cvsection{Most Proud of}
%
%\cvachievement{\faTrophy}{Courage I had}{to take a sinking ship and try to make it float}
%
%\divider
%
%\cvachievement{\faHeartbeat}{Persistence \& Loyalty}{I showed despite the hard moments and my willingness to stay with Yahoo after the acquisition}
%
%\divider
%
%\cvachievement{\faLineChart}{Google's Growth}{from a hundred thousand searches per day to over a billion}
%
%\divider
%
%\cvachievement{\faFemale}{Inspiring women in tech}{Youngest CEO on Fortune's list of 50 most powerful women}


\cvsection[]{Projects}

\nocite{*}

%\cvsubsection{\printinfo{\faChrome}{Web Projects}}
%
%\cvevent{North America Real Estate Stats \hspace{2mm} \cvtag{JS} \cvtag{AWS} \cvtag{Python}}{\href{https://github.com/nathanesau/narealestatestats}{github.com/nathanesau/narealestatestats}}{}{}
%
%\begin{itemize}
%\item Frontend done using nodeJs: ``recharts`` for visualization
%\item Backend done using Django
%\item Some other info abotu this project
%\end{itemize}
%
%\divider

%\cvsubsection{\printinfo{\faDatabase}{Data Science Projects}}

\cvevent{Fantasy Tennis (Python)}{\github{\href{https://github.com/nathanesau/FantasyTennis}{nathanesau/FantasyTennis}}}{}{}

\begin{itemize}
\item Draw Editor for Men's Tennis. Scrapes data from ATP website. Allows user to make predictions on match outcomes.
\end{itemize}

\divider

\cvevent{Rook Card Game (C++)}{\github{\href{https://github.com/nathanesau/RookGame}{nathanesau/RookGame}}}{}{}

\begin{itemize}
\item Implementation of Hasbro's \href{https://en.wikipedia.org/wiki/Rook_(card_game)}{Rook} card game in C++. Qt used for interface. Allows user to play against AI players.
\end{itemize}

\divider

\cvevent{Machine Learning Project (R)}{\github{\href{https://github.com/nathanesau/ukencompetition}{nathanesau/ukencompetition}}}{}{}

\begin{itemize}
\item Applied ML (random forest, gradient boost) to predict mobile app revenue.
\end{itemize}

\divider

\cvevent{Q-Learning TicTacToe (Python)}{\github{\href{https://github.com/nathanesau/TicTacToeRL}{nathanesau/TicTacToeRL}}}{}{}

\begin{itemize}
\item Uses reinforcement learning to train AI to play Tic Tac Toe perfectly.
\end{itemize}

\cvsection{Languages}

\cvskill{C++}{5}
\cvskill{Python}{4}
\cvskill{R}{4}
\cvskill{Java}{2}

% \divider

% \divider
